---
title: "R Notebook"
output: html_notebook
---

```{r}
# libraries

# Globals
global <- list()
```


## quiz 1

```{r}
qz1 <- read.csv("getdata_data_ss06hid.csv")
str(qz1)
```

How many properties are worth $1,000,000 or more?

```{r}
table(qz1$VAL)
```

Download the Excel spreadsheet on Natural Gas Aquisition Program here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx 

```{r}
library(readxl)
dat <- read_excel("~/Projetos/johns hopkins data science specialization/git/3 getting data/getdata_data_DATA.gov_NGAP.xlsx", 
    sheet = "NGAP Sample Data", range = "G18:O23")
View(dat)
```

```{r}
sum(dat$Zip*dat$Ext,na.rm=T)
```

Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 

```{r}
global$url <-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"

library(XML)
global$restaurants <- xmlTreeParse(global$url)

library(xml2)
global$restarants <- read_xml(global$url)
```

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

```{r}
global$url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(global$url, "qz1.5.csv")

library(data.table)
global$DT <- fread("qz1.5.csv")
str(global$DT)
```

The following are ways to calculate the average value of the variable pwgtp15

broken down by sex. Using the data.table package, which will deliver the fastest user time?

```{r}
DT <- global$DT
system.time(mean(DT$pwgtp15,by=DT$SEX))

system.time(DT[,mean(pwgtp15),by=SEX])

system.time({mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)})

system.time(tapply(DT$pwgtp15,DT$SEX,mean))

system.time({rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]})

system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
```

## Quiz 2

Register an application with the Github API here https://github.com/settings/applications. Access the API to get information on your instructors repositories (hint: this is the url you want "https://api.github.com/users/jtleek/repos"). Use this data to find the time that the datasharing repo was created. What time was it created?

This tutorial may be useful (https://github.com/hadley/httr/blob/master/demo/oauth2-github.r). You may also need to run the code in the base R package and not R studio.

```{r}
library(httr)

# 1. Find OAuth settings for github:
#    http://developer.github.com/v3/oauth/
oauth_endpoints("github")

# 2. To make your own application, register at
#    https://github.com/settings/developers. Use any URL for the homepage URL
#    (http://github.com is fine) and  http://localhost:1410 as the callback url
#
#    Replace your key and secret below.
myapp <- oauth_app("rafaelocremix",
  key = "91807422e5ea19a83afe",
  secret = "33a9378f04a5f88c25fc48346cceb009767eb7ca"
)

# 3. Get OAuth credentials
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)

# 4. Use API
gtoken <- config(token = github_token)
req <- GET("https://api.github.com/rate_limit", gtoken)
stop_for_status(req)
content(req)

# OR:
# req <- with_config(gtoken, GET("https://api.github.com/rate_limit"))
# stop_for_status(req)
# content(req)
```

```{r}
library(jsonlite)
jsondata <- fromJSON("https://api.github.com/users/jtleek/repos")
names(jsondata)

subset(jsondata, name == "datasharing")$created_at
```

The sqldf package allows for execution of SQL commands on R data frames. We will use the sqldf package to practice the queries we might send with the dbSendQuery command in RMySQL.

Download the American Community Survey data and load it into an R object called acs

```{r}
global$url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(global$url, "qz2_2.csv")
acs <- read.csv("qz2_2.csv")
```

Which of the following commands will select only the data for the probability weights pwgtp1 with ages less than 50?

```{r}
library(sqldf)
sqldf("select pwgtp1 from acs where AGEP < 50")

# sqldf("select * from acs")
# 
# sqldf("select pwgtp1 from acs")
# 
# sqldf("select * from acs where AGEP <\lt< 50 and pwgtp1")
```

Using the same data frame you created in the previous problem, what is the equivalent function to unique(acs$AGEP)

```{r}
sqldf("select distinct AGEP from acs")
```

How many characters are in the 10th, 20th, 30th and 100th lines of HTML from this page:

http://biostat.jhsph.edu/~jleek/contact.html

(Hint: the nchar() function in R may be helpful)

```{r}
global$connection <- url("http://biostat.jhsph.edu/~jleek/contact.html")
global$biostat <- readLines(global$connection)
close(global$connection)
nchar(global$biostat[c(10,20,30,100)])
```

Read this data set into R and report the sum of the numbers in the fourth of the nine columns.

https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for

Original source of the data: http://www.cpc.ncep.noaa.gov/data/indices/wksst8110.for

(Hint this is a fixed width file format)

```{r}
global$url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for"
download.file(global$url, "qz2_5.csv")
library(readr)
global$qz2.5 <- read_table2("~/Projetos/johns hopkins data science specialization/git/3 getting data/qz2_5.csv", 
    col_types = cols(SST_1 = col_number()), 
    skip = 3)
View(global$qz2.5)

sum(global$qz2.5$SST_1)
```

## Quiz 3

